\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{color}
\hypersetup{colorlinks,breaklinks,
            linkcolor=blue,urlcolor=blue,
            anchorcolor=lue,citecolor=blue}
\input{headerhw.tex}

\chead{\textbf{Discussion 8:}}

\begin{document}

The goals of this discussion section are: 

\begin{enumerate}
\item Work on your homework group problem
\item Get familiar with Probability distributions
\end{enumerate}

Participation in discussion section counts as 5\% of the grade. Completion of the worksheets counts as 20\% of the grade. \textbf{Submit your worksheet work by March 17th at 2:59pm.}

\begin{enumerate}
%where we will chose here $\sigma  = 10$, $\beta = 8/3 $ and $\rho$, proportional to $\Delta T$ will be the parameter to vary (aka test different values).
\item Work on your Homework 5 as a group. Take advantage of this common time to make the most of it (recall it is due by March 17th at 11:59pm). If you have started, use this time to write comments and the code. If you haven't started, take this time to get familiar with the problem and assign roles.
\item Compute the mean $E(x) $ and variance $Var(x)$ of the probability distribution with p.d.f $f(x) = 3x^2$, $0<x <1$. Provide an example of a p.d.f for which $E(x)$ doesn't exist.
%\begin{enumerate}
\item Submit your work (\textbf{only item 2.}) on Catcourses under the assignment \texttt{Worksheet 8} \textbf{as a .pdf}. You will submit your work for item 1. within the assignment \texttt{Homework 5 (group)}.
\end{enumerate}

\end{document}
