\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{color}
\hypersetup{colorlinks,breaklinks,
            linkcolor=blue,urlcolor=blue,
            anchorcolor=lue,citecolor=blue}
\input{headerhw.tex}

\chead{\textbf{Discussion 5:}}

\begin{document}

The goals of this discussion section are: 

\begin{enumerate}
\item Work on your homework group problem
\item Get familiar with Partial Differential Equations
\end{enumerate}

Participation in discussion section counts as 5\% of the grade. Completion of the worksheets counts as 20\% of the grade. \textbf{Submit your worksheet work by February 24th at 2:59pm.}

\begin{enumerate}
%where we will chose here $\sigma  = 10$, $\beta = 8/3 $ and $\rho$, proportional to $\Delta T$ will be the parameter to vary (aka test different values).
\item As group complete Exercise 3.7 from the typed notes \texttt{Math150\_Chapter3.pdf}. Do not spend the entire discussion section on it. 
\item Work on your Homework 3 as a group. Take advantage of this common time to make the most of it (recall it is due by February 24th at 11:59pm). If you have started, use this time to write comments and the code. If you haven't started, take this time to get familiar with the problem and assign roles.
%\begin{enumerate}
\item Submit your work (\textbf{only item 1.}) on Catcourses under the assignment \texttt{Worksheet 5} \textbf{as a .pdf}. You will submit your work for item 2. within the assignment \texttt{Homework 3 (group)}.
\end{enumerate}

\end{document}
