\documentclass[11pt]{article}
\usepackage[normalem]{ulem}
\usepackage{color,hyperref}
\hypersetup{colorlinks,breaklinks,
            linkcolor=blue,urlcolor=blue,
            anchorcolor=lue,citecolor=blue}
\input{headerhw.tex}

\chead{\textbf{Code of conduct for online classes}\ \ \ \ }

\begin{document}

Attending class online is tough, and we will do our best to make this experience the most enjoyable. Let us agree on simple guidelines to make our time together fruitful:

\begin{itemize}
\item We kindly ask you to use your real name on Zoom, and to put a picture of yourself as avatar. We do not require to have the video on as it may be difficult (internet issues, requiring a lot of bandwidth, etc.), but we would like to get to know you, and recognize you later on campus.
\item When working in breakout rooms, we kindly ask you to put your video on at the beginning to meet and greet your fellow group members (then you can turn it off). It is not a requirement. We also kindly ask you to have at least the sound on to introduce yourself and engage in the discussion. If for some reasons you can't have a camera or sound, use actively the chat to communicate with your peers.
\item Keep Zoom up to date. New features are available such as useful non verbal feedback (reaction buttons).
\item We have designed the class to have asynchronous and synchronous portions. When attending lectures or discussion, we appreciate your participation. Use that time as practice and study, be pro-active (ask questions, engage in group activities) so gain the most of it (and have less to do at home outside of class). 
\item The class involves several group assignments, and it highly collaborative. Each formed group (sometimes randomly assigned) will consists of a group speaker/leader (leading the discussion), a note taker (in charge of shared screen and notes), and a time keeper (leading time logistics). Everybody will also be a researcher and must engage in the activity. Everybody should take each role at least once this semester.
\item We understand internet can break, and some days you can't join or stay. We will drop some quizzes and worksheet submissions to cope with unexpected events. 
\item Keep in touch ! Should you have any concern feel free to reach out by email.
\end{itemize}


\end{document}
